### 2014-06-05 writing/S'14 paper/join.tex
Two more items of the paper to do list.

\paragraph{Results.} We found that the RNTN model worked best with 11-dimensional vector representations for the
80 sets and a 90-dimensional feature vector for the classifier. This
model was able to correctly label 99.3\% of the provably derivable test
examples, and 99.1\% of the remaining test examples. The simpler RNN model
worked best with 11 and 75 dimensions, respectively, but was able to
achieve accuracies of only 90.0\% and 87.0\%, respectively.

>>>>

\paragraph{Results.} We found that the RNTN model worked best with 11-dimensional vector representations for the
80 sets and a 90-dimensional feature vector for the classifier, though the performance of the model was
not highly sensitive to either dimensionality parameter in any of the experiments discussed here. This
model was able to correctly label 99.3\% of the provably derivable test
examples, and 99.1\% of the remaining test examples. The simpler RNN model
worked best with 11 and 75 dimensions, respectively, but was able to
achieve accuracies of only 90.0\% and 87.0\%, respectively.

### 2014-06-05 writing/S'14 paper/quantifiers.tex
Two more items of the paper to do list.

% Further explanation for motivation for no/no?

@@

\paragraph{Results.} The results for these experiments are shown in Figure \ref{resultstable}. We compare the results to a most frequent class baseline, which reflects the frequency in the test data of most frequent class in the training data, $\natind$.

\mynote{
The RNN model was approximately optimal with N dimensional word representations and an M dimensional comparison layer. The RNTN was approximately optimal with N and M dimensions, respectively.
% TODO: Update dimensionality
(Note: Models still running. Results might improve and this para is
likely to change.)

@@

Discussion of RNN results (and updated discussion of better RNTN results) to be filled in as results arrive.\\...\\... % TODO
}

>>>>

@@

\paragraph{Results.} The results for these experiments are shown in Figure \ref{resultstable}. We compare the results to a most frequent class baseline, which reflects the frequency in the test data of most frequent class in the training data, $\natind$.
The RNN model was approximately optimal with N dimensional word representations and an M dimensional comparison layer. The RNTN was approximately optimal with N and M dimensions, respectively.
% TODO: Update dimensionality

@@
